# Getting Proper Figure Captions In R Markdown
25 November 2013 

Nicholas J. Gotelli  
Department of Biology  
University of Vermont
___
For reasons I can't understand, R markdown does not produce a figure caption when you ask it to. In order to do this, we have to include the following code for two hooks at the start of the Rmd file:

```{r Captionmaker}
knit_hooks$set(cap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption">', "<b>", options$cap, "</b>", "</p>","\n","___",sep="")
    }
    })
knit_hooks$set(cap.cen = function(before, options, envir) {
  if(!before) {
    paste('<p align="center", class="caption">', "<b>", options$cap.cen, "</b>", "</p>","\n","___",sep="")
    }
    })

```

I've added bold-faced formatting and a single underline to make it easier to distinguish from surrounding text. Now we can add a chunk and insert a caption

```{r CaptionDemo, cap="Figure 1. Here is a sample caption for showing the plotting of 50 consecutive random uniform numbers."}
plot(runif(50),type="b")
```

And here we add a figure with a centered caption, which uses cap.cen:
```{r CaptionDemo2, fig.align='center', cap.cen="Figure 2. Here is a sample caption for a figure that is centered."}
plot(runif(50),type="s")
```
